%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------
\documentclass[margin, centered]{res}
\topmargin=-0.5in
\oddsidemargin -.5in
\evensidemargin -.5in
\textwidth=6.5in
\itemsep=0in
\parsep=0in
\newsectionwidth{1in}
\usepackage[pdftex]{graphicx}
\usepackage{enumitem}
\usepackage{wrapfig}
\usepackage{helvet}
\usepackage[colorlinks = true,
            linkcolor = blue,
            urlcolor  = blue,
            citecolor = blue,
            anchorcolor = blue]{hyperref}
\setlength{\textwidth}{6.5in} % Text width of the document
\setlength{\textheight}{720pt}

\begin{document}

%----------------------------------------------------------------------------------------
%	NAME AND ADDRESS SECTION
%----------------------------------------------------------------------------------------\
\begin{center}
    \hspace{-\hoffset}
    \huge\bf{\href{https://www.about.me/prabhupant}{Prabhu Pant}}
\end{center}
\vspace{-7mm}
\moveleft\hoffset\vbox{\hrule width 19cm height 0.5pt}
\vspace{-9mm}
\begin{center}
    \hspace{-\hoffset}
    \href{mailto:prabhupant09@gmail.com}{prabhupant09@gmail.com} ~\textbullet~ \(+91\) 7408340079 ~\textbullet~ \#E-1031, Rajaji Puram, Lucknow, India
\end{center}
\vspace{-7mm}
\begin{resume}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------
\section{Education}
\textbf{B.Tech in Information Technology, Third Year} \hfill 2015 - 2019 \\
\href{http://gbpuat-tech.ac.in}{College of Technology, Pantnagar, India}
\begin{itemize}
 \item CGPA of {\textbf{{7.11}/10}} (January 2018)
\end{itemize}
\textbf{Senior Secondary School} - \href{http://www.greenfieldsschool.org.in/}{Greenfields School, Lucknow} (ISC) - \textbf{94.8\% }\hfill 2014 - 2015 \\
\textbf{High School} -\href{http://www.greenfieldsschool.org.in/} {Greenfields School, Lucknow} (ICSE) - \textbf{92.8\%} \hfill 2012 - 2013

%----------------------------------------------------------------------------------------
%	EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\section{Experience}


\textbf{Summer Research Intern in Software Engineering Laboratory, \href{https://www.iiitb.ac.in}{IIIT Bangalore}} \\
\emph{Mentored by Prof. Sujit Kumar Chakrabarti, Dept. of CSE, IIIT Bangalore} \hfill June, 2017 - July, 2017 \\
Developed algorithm for automated conversion of MATLAB Simulink models to SMV code for the purpose of model checking and static verification. Implemented a real-life elevator system evaluation model to study model checking in physical world.\

%----------------------------------------------------------------------------------------
%	VOLUNTEER EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\section{Volunteer Experience}


\textbf{Student Volunteer in News and Media, \href{http://nss.nic.in/}{National Service Scheme}} \hfill December, 2017\\
Helped to organise various events aimed at social betterment in poverty-stricken regions of Udham Singh Nagar district of Uttarakhand. Responsible for photographing all the events and preparing articles and news for the local newspaper to bring the problems of the people into limelight.\



%----------------------------------------------------------------------------------------
%	TECHNICAL SKILLS SECTION
%----------------------------------------------------------------------------------------
\section{Technical \hspace{2mm} Skills}
\textbf{Strongest Areas} - Data Structures, Java \\
\textbf{Languages} - Java, Python, C\\
\textbf{Tools/Frameworks} - Android, MySQL, SQLite, Git

%---------------------------------------------------------------------------------------
%	PUBLICATION SECTION
%---------------------------------------------------------------------------------------

\section{Publications}
\begin{itemize}[leftmargin=*]
\item Dinesh Joshi, \textbf{Prabhu Pant}, ``Automated Alert Fencing System Using Arduino and GSM SIM Module'', Indian Journal of Science and Research, vol. 7, issue. 1, January 2018. \href{https://www.ijsr.net/archive/v7i1/ART20179526.pdf}{view here}
\end{itemize}


%----------------------------------------------------------------------------------------
%	RELEVANT COURSES SECTION
%----------------------------------------------------------------------------------------

\section{Relevant \hspace{2mm}Courses}
Data Structures and Algorithms, Discrete Mathematics, Object Oriented Design, Computer Organization, Operating Systems, Software Engineering, Computer Networks

%----------------------------------------------------------------------------------------
%	Selected Projects Section
%----------------------------------------------------------------------------------------
\section{Selected Projects}
All projects available on git : \url{https://www.github.com/prabhupant}
%\setlist[itemize]{
\begin{itemize}[leftmargin=*]
 \item \textbf{\href{https://github.com/prabhupant/java-chatroom}{Java Chat Room}} - A chat server and client written in Java, featuring a swing GUI and MySQL back-end.
 \item \textbf{\href{https://github.com/prabhupant/QuizApp}{QuizApp}} - An Android app for GK quizes.
 \item \textbf{\href{https://github.com/prabhupant/Tetris}{Tetris}} : A basic tetris game written in python. PyQt4 framework was used for GUI programming.
 \item \textbf{\href{https://github.com/prabhupant/footwars}{Footwars}} : A basic EA Sports Fifa 18 score predictor that implements OOP concepts.
 \item \textbf{\href{https://github.com/prabhupant/elevator-model}{Evelator Model}} : A real time simulation of an elevator system made using NuSMV.
 \item \textbf{\href{https://github.com/prabhupant/file-sorter}{File-Sorter}} : A basic GTK GUI based python application to quickly categorize files in a directory based on their types. 


\end{itemize}

%----------------------------------------------------------------------------------------
%	ACHIEVEMENT SECTION
%----------------------------------------------------------------------------------------

\section{Achievements and Awards}
\begin{itemize}[leftmargin=*]
 \item Secured third position in IIT Delhi's RoboTryst Zonal Rounds 2016 held at Pantnagar.
 \item Selected among top 100 photographers to be featured in a photography exhibition under Pune Photo Contest. Organized by {\href{https://www.chiiz.com/}{Chiiz and Mindgraphs}}.
 \item Secured first position in Engima 2016 at College of Technology's annual tech fest Colosseum 2016. Enigma is a quizzing event based on TV shows and movies.
 \item Pan India Blogging Contest Runner-up 2014. Organized by {\href{https://www.indiblogger.in/}{IndiBlogger}}.
 \item Coordinator at Plexus, The Cultural and Technical Society of Department of Information Technology, College of Technology, Pantnagar.
 \item Co-Coordinator at SPIC MACAY, Pantnagar Chapter.


\end{itemize}

%----------------------------------------------------------------------------------------
%	HOBBIES SECTION
%----------------------------------------------------------------------------------------

\section{Hobbies}
Photography, Watching and Reading About Movies, Football, Reading Books, Guitar, Trekking.

%----------------------------------------------------------------------------------------
%	PERSONAL INFORMATION SECTION
%----------------------------------------------------------------------------------------

\section{Personal \hspace{2mm} Information}
\begin{itemize}[leftmargin=*]
 \item Date of Birth: 15 September, 1996
 \item Place of Birth: Lucknow
 \item Languages: Hindi, English
 \item Sex: Male


\end{itemize}

\section{More}
Please visit \href{https://www.about.me/prabhpant}{https://www.about.me/prabhpant}

\end{resume}
\end{document}